---
title: "p8105_hw1_rp3127.rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

## Part 1

```{r Problem 1 basic information}
data("penguins", package = "palmerpenguins")
#read data penguins
head(penguins)
#Find the head of the dataset
nrow(penguins)
#find the row number of the data set
ncol(penguins)
#find the column number of the data set
mean(penguins$flipper_length_mm,na.rm = TRUE)
#find the mean of the flipper length
table(penguins$species)
#show the number of each species of penguins
```
The data is about three species penguins, it includes 8 parameter for each penguins. And there are 344 penguins in total.  From the dataset we know that the mean flipper length is $200.9152$mm.

## Part 2

```{r Problem 2 plot, `echo = FALSE`}
library('ggplot2')
ggplot(penguins,aes(bill_length_mm,flipper_length_mm,color = species))+ geom_point()+ labs(
x ='Bill Length(mm)',
y = 'Fipper Length(mm)',
title = 'Relation between bill length and fipper length for different penguins')
#Plot the graph of the bill length and fipper length and color in species.
ggsave('bill-fipper plot.png', path = 'C:/Users/A/Desktop/R')
#save the ggplot result
```
# Probelm 2

## Part 1

```{r Probelm 2,`echo = FALSE` }
RandomNormal <- rnorm(10,0,1)
#generate 10 value from standard normal distribution
Logical <- randomNormal > 0
#generate the logical vector
CharVec <- c('a','f','e','k','j','1','a','c','5','n')
#generate a character vector
data4 <- c('low','middle','high','middle','middle','middle','low','high','low','low'); FacVec <- factor(data4)
#generate a factor vector with three level
data <- data.frame(RandomNormal,Logical,CharVec,FacVec)
#generate a data frame by the above data
mean(data$RandomNormal)
#find mean of the first vector
mean(data$Logical)
#find mean of the second vector
mean(data$CharVec)
#find mean of the third vector
mean(data$FacVec)
#find mean of the fourth vector
```

We cannot calculates the mean of logical values, character values and factor values. Only the random sample has a mean.

## Part 2

```{r Problem 2,`echo = FALSE`}
as.numeric(data$Logical)
#change the logical value to number
as.numeric(data$CharVec)
#change the character to number
as.numeric(data$FacVec)
#change the level to number
```
Logical values change to $0$ for false and $1$ for true. Character changes to NA unless the characters itself is a number. And level changes to ordered positive integers for each level.